### 2013-02-13 doc/xps2013/proposal.tex
updated nsf support kahan paragraph 	modified:   proposal.tex

\paragraph{Kahan:} Dr. Kahan's research has focused on irregular parallel computation.  Over the course of twelve years, he developed the Tera MTA's multithreaded runtime system and memory allocator still in use today in the Cray XMT, exploring applicability of the system to production codes and benchmarks in the engineering, science, and government domains.  His has been driven by application needs.  The research described herein relies heavily on the experience gained, the innovation being not only to reapply it to mass market technology but also to explore .  He is presently an employee of the Department of Energy.  He has no past or current NSF support.

>>>>

\paragraph{Kahan:} Dr. Kahan's research has focused on irregular parallel computation.  Over the course of twelve years, he developed the Tera MTA's multithreaded runtime system and memory allocator still in use today in the Cray XMT, exploring applicability of the system to production codes and benchmarks in the engineering, science, and government domains.  His research has been driven by real-world application needs, resulting in new algorithms and systems to address concurrency bottlenecks.  He is presently an employee of the Pacific Northwest National Laboratory and an affiliate faculty member of the Computer Science and Engineering Department at the University of Washington.  He has no past or current NSF support.
